### 2014-01-07 msc-thesis/chapters/5/chapter-conclusion.tex
MSC conslusions done.

>>>>

This dissertation has covered a wide range of interests all within indirect conflicts. I have shown how human factors can
be an important part of indirect conflicts and how pairs of developers can be found to be statistically related to indirect
conflicts bugs. I have shown how these human factors can be integrated into indirect conflict tools by using dependencies in 
authored source code artifacts. Ultimately however, these new human factors added into indirect conflict tools resulted in
similar failures of information overload as seen through many previous research tools in indirect conflicts. After these conclusions,
I presented a study which found root causes of indirect conflicts to be contract changes and an unawareness of those changes
implications, that developers use ``Design by Contract'', add and deprecate, and personal experience to avoid indirect conflicts,
and some suggestions for future indirect conflict tool development while stating where gaps in source code analysis should
be improved to improve the indirect conflict tools. Based on that gap in
software evolution analysis in indirect conflicts, I presented a method for finding contextual patterns which can relate to
indirect conflicts in order to aid future tool development for indirect conflicts.

Through the analysis in Chapter 4, I have shown the disjoint of current awareness understanding versus the practical
awareness needs found in industry. This disjoint, caused by the difference of academic and practical understanding in awareness needs,
ultimately lead to tools with information overload and false positive issues. This was quite evident from my tool Impact as
presented in Study 2. Even when the tool is based around the statistical results of Stud 1, the disjoint between what academics
determin developers want versus what they themselves want is quite obvious. The debate of prevention versus cure has been presented along with
the industrial tendency towards curative measures. However, while a curative approach may be favored by developers, further research is needed
to fully asses the positive and negative influences of prevention versus cure for productivity and quality concerns. Finally, I have shown
the gap of analytical evolution tools needed for dependency identification and indirect conflicts. This gap, unless addressed, may prevent
future industrial adoption of tools produced by academia for lack of fit in industrial needs. While, I have shown a potential solution to address
a sub problem of the analysis gap through contextual patterns of indirect conflicts, many sub problems of the analysis gap remian problems
for future research.
